Equilivest: A Robotic Vest to aid in Post-Stroke Dynamic Balance Rehabilitation

### 2022-09-20 iros.tex
Submitted version.

\author{%
Franco Paviotti$^{1}$, Esteban Buniak$^{2}$, Rodrigo Ramele$^{3}$, Orestes Freixes$^{4}$ and Juan Miguel Santos$^{5}$% <-this % stops a space
\thanks{$^{1}$F. Paviotti is with Bioengineering, Instituto Tecnológico de Buenos Aires
                    Buenos Aires, Argentina
        {\tt\small fpaviotti@itba.edu.ar}}%
\thanks{$^{2}$E.Buniak is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires
                    Buenos Aires, Argentina
        {\tt\small ebuniak@itba.edu.ar}}%
\thanks{$^{3}$R.Ramele is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires
                    Buenos Aires, Argentina
        {\tt\small rramele@itba.edu.ar}}%
\thanks{$^{4}$O. Freixes is with the CINER Centro Integral de Neurorehabilitación,
                    Buenos Aires, Argentina
        {\tt\small orestesfreixes@gmail.com}}%
\thanks{$^{5}$J.M. Santos is with the UNAHUR Universidad Nacional de Hurlingham,
                    Buenos Aires, Argentina
        {\tt\small juan.santos@unahur.edu.ar}}%
%\thanks{*This work was not supported by any organization}% <-this % stops a space}
}

@@

\begin{IEEEkeywords}
Stroke, Balance, Rehabilitation, Biofeedback, Vibrotactile
\end{IEEEkeywords}

@@

Patient is a 31 years old female, without any history of chronic ailment, who suffered an acute brainstem stroke after giving birth.  The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which could be linked to pregnancy or puerperium~\cite{Porras.etal2017}.  Patient was in coma for around 2 months, and after that unable to walk, move, talk or swallow.  After two years of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia, which was very important in order to remove the feeding tube allowing her to start speech recovering.

@@

Preliminary results show that for the (1) experiment, on Figure \ref{fig:vestibular}), the value of pitch angles can be used to determine a breakpoint where the fall is inevitable (black vertical line, marked as 1*).   Results from experiment number (2) in Figure \ref{fig:gait} show that the gait cycle is clearly visible from raw acceleration data.

>>>>

\author{%
Franco Paviotti$^{1}$, Esteban Buniak$^{2}$, Rodrigo Ramele$^{3}$, Orestes Freixes$^{4}$ and Juan Miguel Santos$^{5}$% <-this % stops a space
\thanks{$^{1}$F. Paviotti is with Bioengineering, Instituto Tecnológico de Buenos Aires (ITBA)
                    Buenos Aires, Argentina
        {\tt\small fpaviotti@itba.edu.ar}}%
\thanks{$^{2}$E.Buniak is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires (ITBA)
                    Buenos Aires, Argentina
        {\tt\small ebuniak@itba.edu.ar}}%
\thanks{$^{3}$R.Ramele is with Ingeniería en Informática, Instituto Tecnológico de Buenos Aires (ITBA)
                    Buenos Aires, Argentina
        {\tt\small rramele@itba.edu.ar}}%
\thanks{$^{4}$O. Freixes is with the CINER Centro Integral de Neurorehabilitación,
                    Buenos Aires, Argentina
        {\tt\small orestesfreixes@gmail.com}}%
\thanks{$^{5}$J.M. Santos is with the UNAHUR Universidad Nacional de Hurlingham,
                    Buenos Aires, Argentina
        {\tt\small juan.santos@unahur.edu.ar}}%
%\thanks{*This work was not supported by any organization}% <-this % stops a space}
}

@@

\begin{IEEEkeywords}
Stroke, Dynamic Balance, Neurorehabilitation, Biofeedback, Vibrotactile
\end{IEEEkeywords}

@@

Patient is a 31 years-old female, without any history of chronic ailment, who suffered an acute brainstem stroke after giving birth.  The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which could be linked to pregnancy or puerperium~\cite{Porras.etal2017}.  Patient was in coma for around 2 months, and after that unable to walk, move, talk or swallow.  After two years of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia, which was very important in order to remove the feeding tube allowing her to start speech recovering.

@@

Preliminary results show that for the first (1) experiment, on Figure \ref{fig:vestibular}, the pitch angle can be used to determine a breakpoint where the fall is inevitable (black vertical line, marked as 1*).   On the other hand, results from experiment number (2) in Figure \ref{fig:gait} show that the gait cycle is clearly visible from raw acceleration data.
